### 2021-02-06 paper/abstract.tex
Updates and notes for more updates for the introduction.

\noindent Governments worldwide are adopting nuanced policy measures to reduce the
number of Covid-19 cases and to balance social and economic costs. Epidemiological
models have a hard time predicting the effects of fine-grained policies. We propose a
novel simulation-based model to address this shortcoming. We build on state-of-the-art
agent-based simulation models but replace the way contacts between susceptible and
infected people take place. Firstly, we allow for heterogeneity in the types of contacts
(e.g. recurrent or random) and in the infectiousness of each contact type. Secondly, we
strictly separate the number of contacts from the probabilities that a contact leads to
an infection. The number of contacts changes with social distancing policies, the
infection probabilities remain invariant. This allows us to model many types of targeted
policies that cannot be incorporated into other models. To validate our model, we show
that it can predict the effect of the German November lockdown even if no similar policy
has been observed during the time period that was used to estimate the model parameters.

>>>>

\noindent
Governments worldwide have been adopting various and nuanced policy measures
to reduce the number of Covid-19 cases.
However, epidemiological models usually lack sufficient detail in meeting
patterns to credibly predict the effects such policies, much less predict
complementarities or substitution effects between them.
We propose a novel simulation-based model to address these shortcomings.
We build on state-of-the-art agent-based simulation models, greatly increasing
the amount of detail and realism with which contacts take place.
Firstly, we allow for heterogeneity in the types of contacts (e.g. recurrent and
non-recurrent) and in the infectiousness of each contact type.
Secondly, we strictly separate the number of contacts from the probabilities
that a contact leads to an infection.
Thus, social distancing policies can affect the number of contacts while the
infection probabilities remain invariant.
This allows us to model many types of targeted policies that cannot be
incorporated into other models.
\textcolor{red}{
To validate our model, we show that it can predict the effect of the German
November lockdown even if no similar policy has been observed during the time
period that was used to estimate the model parameters.
}

### 2021-02-06 paper/introduction.tex
Updates and notes for more updates for the introduction.

The first wave of the Covid-19 pandemic prompted strict lockdowns and restrictions
across the world. Many countries were able to contain the spread of the virus and to
relax restrictions during midyear. At the same time, the social and economic costs were
enormous. In the second wave, countries are trying to implement more nuanced policies.
For example, Germany imposed a ``lockdown-light'' in November. Some businesses are
closed and certain leisure activities are prohibited but educational facilities remain
open.

Current epidemiological models have not been designed to predict the effect of
fine-grained policies. The models need to be extended for each new policy proposal and
cannot be easily adapted to fast changing environments. This report describes a model
that has been designed from the ground up to predict the effects of contact reducing
policies in real time. It has the following features:

@@

This report describes the model in an abstract way, but uses many realistic examples
from a version that is specialized to Germany. It is important to note that this
specialization is not baked into the model or the Python code. It is easy to adjust the
model to other countries if data on the number of contacts and a dataset with background
characteristics are available.

More details about the German model as well as applications to currently discussed
German policies can be found in \citet{Dorn2020a}.

>>>>

% setting
The first wave of the Covid-19 pandemic prompted strict lockdowns and restrictions
across the world.
At large social and economic costs, these strict measures were able to suppress the
spread of the disease and allowed governments to relax restrictions over the summer.
Governments were more hesitant and imposed less restrictive policies when infections
started to soar again in the fall.
For example, Germany imposed a ``lockdown-light'' in November, closing fewer businesses
than in spring and leaving schools open. Mobility data also showed that individuals
reduced their mobility much less than during the first lockdown.

\textcolor{red}{Add image of Google Mobility reductions!}

% challenge
The less restrictive lockdown led only to a stagnation of cases and led many experts
\textcolor{red}{(Cite No-Covid, Zero-Covid, Leopoldina, Lancet...)} to call for a
strict lockdown to bring cases back to very low levels, such as single digit incidences.
These calls have received additional attention since new and more contagiuos variants
have emerged in several countries and increased the urgency to reduce transmission
dynamics and increased awareness for the mutagenic potential of high incidences.
\textcolor{red}{Add citations!}

However, epidemiological models are not suited to advise which combination of policies
would be able to bring infections down to sustainable levels.
As they have not been designed to predict the effects of fine-grained policies,
they need to be extended for each new policy proposal.
Nor can they show the trade-offs, substitutability or complementarity of policies.

% contribution
This report describes a model that has been designed from the ground up to predict the
effects of contact reducing policies in real time. It has the following features:

@@

This report describes the model in an abstract way, but uses many realistic examples
from a version that is specialized to Germany. It is important to note that it would
be easy to adjust the model to other countries if data on the number of contacts and
a dataset with background characteristics are available.

More details about the German model as well as applications to currently discussed
German policies can be found in \citet{Dorn2020a}.
\textcolor{red}{Update citation to home office report.}
